---
title: "Data Cleaning"
output: html_document
---

```{r, include=FALSE}
setwd("~/Desktop/Framwork 2/Project")
raw_data=read.csv('RawData.csv')
```

# Explore data
The dataset contains 34 variables regarding wine reviews with 1231 observations.
```{r}
str(raw_data)
```

## Select variables for analysis
We can eliminate any variables that we found not useful such as asins, dateAdded, dateUpdated, descriptions, dimension, ean, flavors, keys, reviews.date, reviews.dateAdded, reviews.dateSeen, reviews.didPurchase, reviews.sourceURLs, sizes, sourceURLs, upc

```{r}
raw_data2 = raw_data[,-c(2,5:11,17:20,25,31:33)]
str(raw_data2)
```

## Check for missing values
By using is.na( ), we found that the data contains missing values. However, some observations in the factor variables were recored as “” (or blank), which could not be detected by is.na( ). Therefore, we had to check for those blank values in each column in the next step.
```{r}
any(is.na(raw_data2))
sum(is.na(raw_data2))
```

## Check for missing values in numerical variables
0% of data are missing for the variable reviews.rating
41% of data are missing for the variable reviews.id
62.55% of data are missing for the variable reviews.numHelpful
49.47% of data are missing for the variable reviews.doRecommend
```{r}
sum(is.na(raw_data2$reviews.rating))/nrow(raw_data2)*100
sum(is.na(raw_data2$reviews.id))/nrow(raw_data2)*100
sum(is.na(raw_data2$reviews.numHelpful))/nrow(raw_data2)*100
sum(is.na(raw_data2$reviews.doRecommend))/nrow(raw_data2)*100
```

## Check for missing values in factor variables
Since some blank observations were recorded as "", we could not detect them with is.na( ).
Thus, we will explore how many "" appeared in each variable and counted them as missing values.
```{r}
#id
sum(raw_data2$id == '')/nrow(raw_data2)*100 #0%

#brand
sum(raw_data2$brand == '')/nrow(raw_data2)*100 #0%

#categories
sum(raw_data2$categories == '')/nrow(raw_data2)*100 #0%

#manufacturer
sum(raw_data2$manufacturer == '')/nrow(raw_data2)*100 #63.03818%

#manufacturerNumber
sum(raw_data2$manufacturerNumber == '')/nrow(raw_data2)*100 #22.25833%

#name
sum(raw_data2$name == '')/nrow(raw_data2)*100 #0%

#primaryCategories
sum(raw_data2$primaryCategories == '')/nrow(raw_data2)*100 #0%

#quantities
sum(raw_data2$quantities == '')/nrow(raw_data2)*100 #85.29651%

#reviews.text
sum(raw_data2$reviews.text == '')/nrow(raw_data2)*100 #0.08123477%

#reviews.title
sum(raw_data2$reviews.title == '')/nrow(raw_data2)*100 #3.086921%

#reviews.userCity
sum(raw_data2$reviews.userCity == '')/nrow(raw_data2)*100 #93.34%

#reviews.userProvince
sum(raw_data2$reviews.userProvince == '')/nrow(raw_data2)*100 #99.26889%

#reviews.username
sum(raw_data2$reviews.username == '')/nrow(raw_data2)*100 #0.08123477%

#weight
sum(raw_data2$weight == '')/nrow(raw_data2)*100 #42.97319%
```

Since reviews.id, reviews.numHelpful, reviews.doRecommend, manufacturer, manufacturerNumber quantities, reviews.userCity, reviews.userProvince, and weight have significant amount of missing data (more than 10%), we decide to drop these variables.
```{r}
library(dplyr)
library(tidyverse)
raw_data3 <- select(raw_data2, -reviews.id, -reviews.numHelpful, -reviews.doRecommend,-manufacturer, -manufacturerNumber, - quantities, - reviews.userCity, -reviews.userProvince, - weight)

str(raw_data3)
```

We discard the rows containing missing values for reviews.text, reviews.title, and reviews.username because there are not many missing values. We now have 9 variables with 1191 observations.
```{r}
raw_data4 = raw_data3
raw_data4 = raw_data3[!(raw_data3$reviews.text == '' | raw_data3$reviews.title == '' | raw_data3$reviews.username == ''),]
str(raw_data4)
```


To confirm that there was no “” left in those variables.
```{r}
sum(raw_data4$reviews.text == '')
sum(raw_data4$reviews.title == '')
sum(raw_data4$reviews.username == '')
```

For the categorical variable 'brand', there are over 100 categories while some categories contain only 1 observation. Therefore, we regroup the brand by keeping the top 20 brands and assigning the rest to 'other'.
We then have 21 brand categories in total. 
```{r}
raw_data4$brand2=raw_data4$brand
class(raw_data4$brand2)
raw_data4$brand2=as.character(raw_data4$brand2)
raw_data4$brand2=ifelse(raw_data4$brand2!='Jim Beam' &raw_data4$brand2!='Bittermens' &raw_data4$brand2!='Vintage Wine Estates'
                 &raw_data4$brand2!='Master of Mixes'&raw_data4$brand2!='Cocktail Artist'&raw_data4$brand2!='Clamato'
                 &raw_data4$brand2!='Zing Zang'&raw_data4$brand2!='Mr. & Mrs. T' &raw_data4$brand2!='Dirty Sue' 
                 &raw_data4$brand2!='Jose Cuervo'
                 &raw_data4$brand2!='Sauza'&raw_data4$brand2!='Jim Beam Black'&raw_data4$brand2!='Powell Mahoney'
                 &raw_data4$brand2!="Jack Daniel's"&raw_data4$brand2!='Goya Food'
                 &raw_data4$brand2!='Pinnacle'
                 &raw_data4$brand2!='Wine Cube153'&raw_data4$brand2!='KNOB CREEK'&raw_data4$brand2!='Cobblestone Bread Co.'
                 &raw_data4$brand2!="Angostora","Other",raw_data4$brand2)
raw_data4$brand2=as.factor(raw_data4$brand2)
table(raw_data4$brand2)

```


## Export the clean data to .csv file
```{r}
write.csv(raw_data4, 'cleaned_data.csv')
```

